Architectures and Open pNets

### 2018-10-11 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: Updated the the Failure Monitor example (Fig. 1) and the explanation following the def of components

\usepackage{amsmath,amsthm,amscd}
\usepackage{amssymb}    % for blackboard B
\usepackage{rotating}   % to rotate the figures
\usepackage{mathpartir} % math paragraph + inference rules
\usepackage{mathtools}  % for align, multline etc.
\usepackage{caption}
\usepackage{xifthen}
\usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)

@@

The model in \fig{schema:ArchFailure:BIP} has three components.  The
component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
it only has its interface defined: $(\emptyset, \{\PortFinish,
\PortResume, \PortFail\}, \export[\emptyset])$, with
$\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
\PortResume, \PortFail\}$.  The other two components, $\NameCtrl$ and
$\NameTimer$, are \emph{coordinators}\mdash they are specified
completely, including the states and transitions defining their
\emph{behaviour}.  Transitions are labelled with the ports of the
corresponding components, Boolean guards and update assignments on local
variables.  For instance, the loop transition $\tstate{1}
\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
$\NameTimer$ component is labeled by the port $\PortTick$, it can be
fired only when the current value of the local variable $t$ is less
than $z.u$, where $z = [l, u]$ is a local variable representing an
interval.  Upon firing, this transition increments the value of $t$ by
$1$.  The guard and update assignment of the transition $\tstate{1}
\goesto{\PortResume} \tstate{0}$ are omitted.  The default values are
the constant predicate $\true$ and the empty assignment {\emptyassign}
%$\mathit{skip}$ operator
respectively.  The initial states \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{z
\mapsto \topinterval, t \mapsto 0\}$ and $\val{0}{\NameCtrl} =
\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
$\goesto{\IntervalInit[]} \cstate{0}$, respectively.  The constants
$\mathrm{Min}$ and $\mathrm{Max}$ are the parameters of the
architecture.
%\noteLH{It looks like Max is in zone, I do not understand}

>>>>

\usepackage{amsmath,amsthm,amscd}
\usepackage{amssymb}    % for blackboard B
\usepackage{rotating}   % to rotate the figures
\usepackage{mathpartir} % math paragraph + inference rules
\usepackage{mathtools}  % for align, multline etc.
\usepackage{caption}
\usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)

@@

The model in \fig{schema:ArchFailure:BIP} has two components:
%% The
%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
%% it only has its interface defined: $(\emptyset, \{\PortFinish,
%% \PortResume, \PortFail\}, \export[\emptyset])$, with
%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
%% \PortResume, \PortFail\}$.  
%% The other two components,
%
$\NameCtrl$ and $\NameTimer$, with interfaces
\[\bigl(
\{\mathit{zone}\},
\{\PortReset, \PortFail, \PortResume, \PortTO\},
\export[\NameCtrl]
\bigr)\]
and
\[\bigl(
\{t, z\},
\{\PortTick, \PortCancel, \PortTO\},
\export[\NameTimer]
\bigr)\]
%
respectively, where $\export[\NameCtrl](\PortFail) =
\{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
$\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
Variable $t$ is implicitly assumed to be an integer.  Variables $z$
and $\mathit{zone}$ are implicitly assumed to be integer intervals of
the form $[l,u]$.  For both types, we also implicitly assume the
natural ordering: increasing integers and interval inclusion.

%% are \emph{coordinators}\mdash they are specified
%% completely, including the states and transitions defining their
%% \emph{behaviour}.
Component \emph{behaviour} is defined by states ($\cstate{0},
\cstate{1}, \cstate{2}$, for $\NameCtrl$, and $\tstate{0}$, for
$\NameTimer$) and transitions.
%
Transitions are labelled with the ports of the
corresponding components, Boolean guards and update assignments on local
variables.  For instance, the loop transition $\tstate{0}
\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
$\NameTimer$ component is labeled by the port $\PortTick$, it can be
fired only when the current value of the local variable $t$ is less
than $z.u$.
%% , where $z = [l, u]$ is a local variable representing an
%% interval
Upon firing, this transition increments the value of $t$ by $1$.  The
guards and update assignments of the transitions of $\NameCtrl$ are
omitted.  The default values are the constant predicate $\true$ and
the empty assignment {\emptyassign}, respectively.  The initial states
\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
$\goesto{\IntervalInit[]} \cstate{0}$, respectively.\footnote{%
%
  We use $\topinterval$ to denote the top interval in the inclusion
  order, \ie $(-\infty, +\infty)$.
%
} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
of the architecture.
%\noteLH{It looks like Max is in zone, I do not understand}
